---
title: ""
format: 
  html:
    page-layout: custom
    theme: journal
    css: custom.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- "https://docs.google.com/spreadsheets/d/1CBVoZB-KrsoQyBe1xEEDdMF2ESj8IoaKrdzPdv3oFMs/edit#gid=917338460"
cv <- googlesheets4::read_sheet(cv_url)
```

<!-- Sidebar/column -->

<!-- Please refer to Page Layout section in Quarto docs (specifically the part on CSS Grid) - https://quarto.org/docs/output-formats/page-layout.html#custom - to customise column positions -->

::: {.grid}

::: {.g-col-3 .g-start-2}

<br>

### Contact

<span style="font-size: 1.5em;"> <a href='https://jhylin.github.io/Data_in_life_blog/' target='_blank'> <i class="fa fa-home"></i></a> <a href='https://github.com/jhylin' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:jennyhylin@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://twitter.com/jenhylin' target='_blank'><i class="fa-brands fa-twitter"></i></a> <a href='https://www.linkedin.com/in/jennifer-hy-lin-a9b86981/' target='_blank'><i class="fa-brands fa-linkedin"></i></a></left>
</span>

<!-- Uncomment and add contents in the column on the left if needed -->

<br>

### Programming skills

<i class="fa-brands fa-python"></i> Python <br> <i class="fa-solid fa-table"></i> Polars <br> <i class="fa-solid fa-table-cells"></i> Pandas <br> <i class="fa-solid fa-chart-column"></i> Matplotlib <br> <i class="fa-solid fa-computer"></i> scikit-learn <br> <i class="fab fa-r-project"></i> R <br> <i class="fa-solid fa-chart-line"></i> tidyverse <br> <i class="fab fa-markdown"></i> RMarkdown / Quarto <br> <i class="fa-solid fa-database"></i> SQL <br> <i class="fa-solid fa-table-columns"></i> Tableau <br> <i class="fas fa-code-branch"></i> Git <br> <i class="fab fa-github"></i> GitHub <br> 

:::

<!-- Column for main content -->
::: {.g-col-6 .g-start-5}

<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}
col_br_loc <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<br><i class="fa-solid fa-location-dot"></i> ', col),
      ""
    )
}
create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", NA_character_, loc)) |>
    dplyr::filter(in_resume %in% c("TRUE"), section == section_name) |>
    dplyr::select(section:description_1) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Current <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> {col_br(institution)} {col_br(description_1)} {col_br_loc(loc)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, loc, description_1)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text)
}
```

<!-- Main content -->

<br>

# Jennifer HY Lin

## <i class="fa-solid fa-diagram-project"></i> Data analytics projects

```{r}
create_section(cv, "data_analytics_projects")
```

## <i class="fa-solid fa-certificate"></i> Certification

```{r}
create_section(cv, "certification")
```

## <i class="fa-solid fa-handshake-angle"></i> Volunteering work

```{r}
create_section(cv, "volunteering")
```

## <i class="fa-solid fa-briefcase"></i> Work experience

```{r}
create_section(cv, "experience")
```

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_section(cv, "education")
```

## <i class="fa-solid fa-book"></i> Publications

```{r}
create_section(cv, "publications")
```
:::


:::

<!-- footer -->

<footer>
<p class = "footer">
CV made with ❤️ and [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available from <i class="fa-brands fa-github"></i> [GitHub](https://github.com/jhylin/CV_resume_quarto/blob/main/index.qmd) with original source code from <i class="fa-brands fa-github"></i> [GitHub](https://github.com/beatrizmilz/resume/blob/master/docs/index.qmd). <br>License: [CC BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/).
</p>
</footer>

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
